LLM-Driven CIDOC-CRM Knowledge Graph Extraction from Museum Archives

### 2025-05-05 paper/paper.tex
paper: ontology diagram
paper: specify LM Studio deployment

@@

\begin{table}[h]
    \centering
    \caption{Models used for Knowledge Graph Generation} % Updated caption slightly
    \label{tab:model_deployment}
    \begin{tabular}{ll}
        \hline
        Model        & Deployment         \\
        \hline
        Qwen 2.5 3B  & Ollama on RTX 3060 \\
        Llama 3.2 3B & Ollama on RTX 3060 \\
        Qwen 2.5 7B  & LM Studio          \\
        Llama 3.1 8B & LM Studio          \\
        DeepSeek V3  & DeepSeek Platform  \\
        DeepSeek R1  & DeepSeek Platform  \\
        \hline
    \end{tabular}
\end{table}

>>>>

\begin{figure}[!t]
    \centering
    \includegraphics[width=3in]{assets/ontology}
    \caption{CIDOC-CRM Ontology}
    \label{fig_ontology}
\end{figure}

@@

\begin{table}[h]
    \centering
    \caption{Models used for Knowledge Graph Generation} % Updated caption slightly
    \label{tab:model_deployment}
    \begin{tabular}{ll}
        \hline
        Model        & Deployment            \\
        \hline
        Qwen 2.5 3B  & Ollama on RTX 3060    \\
        Llama 3.2 3B & Ollama on RTX 3060    \\
        Qwen 2.5 7B  & LM Studio on RTX 5090 \\
        Llama 3.1 8B & LM Studio on RTX 5090 \\
        DeepSeek V3  & DeepSeek Platform     \\
        DeepSeek R1  & DeepSeek Platform     \\
        \hline
    \end{tabular}
\end{table}
